SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-01 docs/questioning.tex
some changes

Here we analyze the {\sc tba} different protection approaches.
Note that most mechanisms that belong to this category have
not been extensively tested in terms of diagnostic performance.

@@

This approach is used to detect attacks that target web users.
When using a framework that implements
this approach, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that intercepts
server responses. Policy enforcement is one of the two
approaches (the other is Securing Mashups --- see
Subsubsection~\ref{sec:mashups}) that is
used to prevent {\sc csrf} attacks.

@@

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support this
functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}. The main problem with
the above mechanisms is that they are vulnerable
to non-persistent {\sc xss} attacks that alter
the {\sc dom} of an already rendered
page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
~\cite{APKLM10}.

@@

\noindent
{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
can actually detect such an attack (along with some architectures
presented in Subsubsection~~\ref{sec:mashups}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site. As a result,
{\sc soma} can also detect {\sc csrf} attacks.

@@

\subsubsection{Securing Mashups}
\label{sec:mashups}

% {\it WebJail}~\cite{VDDPJ11}, overcomes this issue
% by containing the functionality of third-party scripts.

@@

  \multirow{11}{*}{Policy Enforcement}

@@

  \multirow{3}{*}{Securing Mashups}
  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\

@@

 We need to mention that there are mechanisms that
 do not need to be established purely through testing
 Since they provide systematic arguments as to why
 the design is secure against attacks.

@@

  \multirow{3}{*}{Securing Mashups}
  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\

>>>>

Here we analyze the three basic design-based approaches
used to protect web applications from the attacks we
discussed in Section~\ref{sec:attacks}.

@@

This approach is used to detect attacks that target web users.
When using a framework that implements
this approach, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that intercepts
server responses.

@@

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support this
functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}. The main problem with
the above mechanisms is that they are vulnerable
to non-persistent {\sc xss} attacks that alter
the {\sc dom} of an already rendered
page~\cite{APKLM10}.

@@

\noindent
{\it WebJail}~\cite{VDDPJ11}, and
{\sc soma}~\cite{OWVS08} are two frameworks that
can actually detect such an attack (locus {\sc x}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site. As a result,
{\sc soma} can also detect {\sc csrf} attacks.
WebJail contains the functionality of third-party scripts
by introducing a web component integrator that restricts
the access that these scripts may have to either the data
or the functionality of other components.

@@

@@

  \multirow{12}{*}{Policy Enforcement}

@@

  % \hline
  % \hline 
  % \multirow{3}{*}{Securing Mashups}
  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\

@@

Notes:
\begin{enumerate}
\item Note that most mechanisms that implement design-based
approaches have not been extensively tested in terms of
diagnostic performance.
\item We need to mention that there are mechanisms that
do not need to be established purely through testing
Since they provide systematic arguments as to why
the design is secure against attacks.
\item Policy enforcement is the
only approach that is
used to prevent {\sc csrf} attacks.
\item See j{\sc csrf} for {\sc soma}'s drawbacks.
\end{enumerate}

@@

  % \hline
  % \hline 
  % \multirow{3}{*}{Securing Mashups}
  % &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
